IML Term project

### 2022-12-06 main_markdown.rmd

>>>>

### SVM (first version of actual model)
```{r svm2}
tc<-tune.control(cross=464)
tuner<-tune(svm,class2~., data=npf.168.fact, kernel="linear",type="C", ranges = list (cost = seq(0.01,0.05,0.01)), tunecontrol = tc)
bpam<-tuner$best.parameters
preds<-c()
perps<-c()
for(i in 1:464){
  newexp<-npf.168.fact[-i,]
  newmod<-svm(class2~., newexp,kernel="linear",cost=bpam[1,1],scale=F, probability=T, type="C")
  newprob<-predict(newmod, newdata=npf.168.fact[i,1:36],probability=T)
  if(class2[i]==1){
    newperp<-attr(newprob, "probabilities")[1,1]
  } else{
    newperp<-attr(newprob, "probabilities")[1,2]
  }
  perps<-c(perps,log(newperp))
  preds<-c(preds, newprob[1])
}
mean((preds-1)==class2)
exp(-mean(perps))
```
